---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- devtools::build_readme() -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/natverse/coconat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/natverse/coconat/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/natverse/coconat/branch/master/graph/badge.svg)](https://app.codecov.io/gh/natverse/coconat?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of *coconat* is to provide dataset agnostic support for connectome analysis.

It is intended to have a mix of end-user functionality and functions that are
principally intended as building blocks for more specialised packages such as
https://natverse.org/neuprintr/ or https://natverse.org/fafbseg/.

It is also a key building block for the [https://natverse.org/coconatfly](coconatfly)
package,
which provides a small number of powerful functions for comparative connectomics
analysis of dense reconstructions of *Drosophila* brain and VNC data.

## Installation

You can install the development version of coconat from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("natverse/coconat")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(coconat)
# da2ds=neuprintr::neuprint_connection_table('DA2_lPN', details=TRUE, partners='out', conn = hbconn)
da2ds=readRDS(system.file('sampledata/da2ds.rds', package = 'coconat'))
head(da2ds)
```

```{r}
library(Matrix)
am=partner_summary2adjacency_matrix(da2ds, inputcol = 'bodyid', outputcol = 'partner')
image(am)
```

```{r}

am2=partner_summary2adjacency_matrix(subset(da2ds, weight>=15), 
                                     inputcol = 'bodyid', outputcol = 'partner')
image(am2)
```
Now we can also cosine cluster


We can do this for the inputs (the 5 PNs should look much the same)
```{r}
heatmap(cosine_sim(am, transpose = T))
```

Or the outputs

```{r}
heatmap(cosine_sim(am))
```

But it would of course be more useful if we did this based on a richer set of inputs

