---
title: "identifiers-and-datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{identifiers-and-datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(coconat)
```

## datasets
coconat needs to be able to handle a range of datasets. For each dataset we 
record both a long name and a short name (2 characters [a-z0-9]) that we use to 
refer to them.

You can tell coconat about a new dataset by doing:

```{r, eval=FALSE}
register_dataset('flywire', shortname = 'fw', species = 'Drosophila melanogaster', sex = 'F')
```

## identifiers and keys

Each dataset will have unique identifiers for the neurons that it contains. All
connectomics data sources that we currently work with have identifiers within
the 64 bit integer range, but there is no reason that they cannot contain
additional characters. To ensure interoperability, we will

1. default to handling all identifiers as character vectors (strings) even if
the native form in a package providing access to a dataset is some king of
numeric.
2. introduce the notion of a *key* in the form `"<dataset>:<id>"`

The second point is vital since the same numeric identifier can be used in 
different datasets to refer to different neurons.

We provide a number of functions to assist with this. At the most basic level
`id2char()`will convert numeric ids to a character representation taking care of
issues like the fact that `as.character(1e5)`=`r as.character(1e5)` which can 
cause trouble.

```{r}
id2char(1000)
id2char(1e5)
id2char(NA)
id2char(bit64::as.integer64('12345678901234'))
```


